\thesistitle

### 2019-06-26 sections/research.tex
Clone types summarized

\subsection{Type 2R clones}
Type 2R clones are modelled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments. For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones (as shown in figure \ref{fig:type2} previously). Refactoring such clones can be harmful instead of helpful.

@@

$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
$$Total = \text{Total number in the clone instance}$$
$$l = \text{Number of literals}$$
$$v = \text{Number of variables}$$
$$m = \text{Number of method calls}$$
$$t = \text{Number of tokens}$$

@@

$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
$$Statements = \text{The amount of statements in this code fragment}$$
$$C_{gap} = \text{The gap between two clones}$$
$$C_{above} = \text{The clone instance above the gap}$$
$$C_{below} = \text{The clone instance below the gap}$$

@@

@@

\subsubsection{Validating the type 2 variability threshold}

>>>>

\subsection{Type 2R clones} \label{sec:type2r}
Type 2R clones are modelled after type 2 clones, which allow any change in identifiers, literals, types, layout, and comments. For refactoring purposes, this definition is unsuitable; if we allow any change in identifiers, literals, and types, we cannot distinguish between different variables, different types and different method calls anymore. This could render two methods that have an entirely different functionality as clones (as shown in figure \ref{fig:type2} previously). Refactoring such clones can be harmful instead of helpful.

@@

\begin{eqfloat}\label{eq:type2r}
$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
$$Total = \text{Total number in the clone instance}$$
$$l = \text{Number of literals}$$
$$v = \text{Number of variables}$$
$$m = \text{Number of method calls}$$
$$t = \text{Number of tokens}$$
\caption{Type 2R variability threshold formula}\end{eqfloat}

@@

\begin{eqfloat}\label{eq:type3r}
$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
$$Statements = \text{The amount of statements in this code fragment}$$
$$C_{gap} = \text{The gap between two clones}$$
$$C_{above} = \text{The clone instance above the gap}$$
$$C_{below} = \text{The clone instance below the gap}$$
\caption{Type 3R clone merge opportunities threshold formula}\end{eqfloat}

@@

\subsection{Clone types summarized}
The given clone definitions (types 1R, 2R and 3R) are refactoring-oriented in the sense that they were designed after the literature type definitions but with a concrete refactoring opportunity in mind. Summarized, these types can be explained as follows:

Type 1R: Allows no difference between cloned fragments, making it possible to refactor both fragments to a method call that contains the code of both locations.
Type 2R: Allows difference between cloned fragments in controlled features of a codebase. Refactoring opportunities for these controlled features are known, allowing refactoring with a minor tradeoff.
Type 3R: Allows any difference. When refactored, this difference must be wrapped in its own block, which entails a major tradeoff.

@@

\subsubsection{Validating the type 2R variability threshold}
In the definition of type 2R (see section \ref{eq:type2r}) clones we described how type 2R clones work on basis of a variability threshold. This threshold,
